\chapter{Introduction}
\label{ch:intro}

\glspl{wfms} empower business process automation \citep{Zeng2005}. One crucial aspect of this empowerment consists in effectively assigning jobs to users in \glspl{wfms} \citep{Zeng2005}. This concept is termed role resolution in the literature \citep{Cheng2000}. Solving the role resolution problem in \glspl{wfms} can lead to fully realize the potential gains such as:
\begin{enumerate*}
	\item Cost savings
	\item Fairness in workload assignment
	\item Optimal resources usage.
\end{enumerate*}

Currently most \glspl{wfms} implement elementary role resolution policies \citep{Zeng2005}. Expanding on \citet{Zeng2005}'s work, this thesis focuses on further developing traditional \gls{milp} based approaches and proposes novel \gls{rl} based methods for solving the role resolution problem in \glspl{wfms}.


\section{Objectives}
\label{sec:objectives}

The objectives of this thesis build upon the work of \citet{Zeng2005} in which they describe policies for optimal role resolution in \glspl{wfms} and extends these capabilities from a twofold perspective:
\begin{enumerate*}
	\item Further develops the \gls{milp} based approaches proposed by \citet{Zeng2005}
	\item Explores the capabilities offered by \gls{rl} as in order to overcome the deterministic limitations of traditional \gls{milp} based methods by approaching role resolution in \glspl{wfms} from a stochastic perspective.
\end{enumerate*}

Formally, this thesis tries to answer the following research questions:

\begin{enumerate}[label=\textbf{Q. \Roman*},ref=Research Question \Roman*]
\item Can current optimization methods for job assignment in workflow processes be further developed? \label{rq:one}
\item Are there state of the art approaches that can complement job assignment with mathematical optimization methods? \label{rq:two}
\end{enumerate}

\section{Thesis Structure}

This thesis is subdivided in seven main chapters:

\begin{itemize}
	\item \chpref{ch:related_work} gives an overview of the state of the art literature in the touched thematic topics of this work.
	\item \chpref{ch:foundations} outlines the theoretical foundations in \gls{bpmn}, \glspl{wfms}, their limitations and role resolution. 
	\item \chpref{ch:discrete_event_sim} maps the theoretical concepts outlined in \chpref{ch:foundations} with the actual discrete event simulation framework used for evaluation. It explains in detail the governing logic of the subset of \gls{bpmn} elements implemented and the role resolution approach used.
	\item \chpref{ch:policies} initially describes in detail the \gls{milp} based approach used in this thesis and how traditional methods have been extended, followed by a theoretical introduction in \gls{rl} which is eventually used in the culminating part where the \gls{rl} based approaches are explained.
	\item \chpref{ch:empirical_analysis} describes the evaluation framework implemented, how both role resolution approaches are simulated and defines the \glspl{kpi} used to measure them.
	\item \chpref{ch:results} initially exposes the results obtained by the \gls{milp} based methods and then compares them with the traditional methods of \citet{Zeng2005}. Subsequently, the results of the \gls{rl} based methods are also outlined.
	\item \chpref{ch:conclusion} is the culminating chapter in which the results obtained in \chpref{ch:results} are critically discussed and interpreted, then	a summary of the key findings of the thesis is outlined and the research questions posed in \secref{sec:objectives} are answered by looking at the actual usability, limitations and to whom the results are most applicable to. Finally consequences and outlooks about the future trends and how the empirical results of this thesis can be extended by prospective researchers are given.
\end{itemize}