\begin{acknowledgements}

I would like to thank Prof. Dr. Daning Hu for giving me the marvelous opportunity of pursuing this topic in collaboration with immopac ag and supporting me all along the path with his invaluable flexibility.

I am deeply grateful and eternally indebted to Dr. Markus Uhr for his terrific knowledge, availability, patience, comprehension and guidance during the course of this thesis. His keen eye for details, both technical and not are the foundations on which this thesis is based. His tremendous patience and capability to convey difficult concepts in a pragmatic fashion were key factors for the successful completion of this work. Lastly, I am also grateful to Dr. Markus Uhr for proofreading this thesis.

I am enormously grateful to both Dr. Robert H\"ohener and Dr. Thomas H\"ohener for advocating for this collaborative project and for allowing me to conduct this research at immopac ag. Moreover I want to thank Dr. Robert H\"ohener for his invaluable feedback during the initial phase of this thesis and administrative consultation.

I am grateful to Dr. Andreas Horni for his technical suggestions and feedback on the \latex structure and for proofreading this thesis.

My deepest gratitude goes towards my parents, Dr. med. Tatjana Zafirovska and Ljupco Ko\v{c}ovski for believing in me as a person and for always motivating me to pursue my dreams and push my boundaries.

My warmest thankfulness goes to Martina Lardi for her academic feedback, patience, comprehension during the whole duration of this project and for proofreading this thesis.

I want to thank Dustin Kerner for proofreading the German parts of this work.

Ultimately I want to thank the whole staff of immopac ag for their continuous support during the course of my work and for their interest in this thesis.

\end{acknowledgements}